---
title: "Fiji Earthquake Data"
output: github_document
---

### Choose and load desired dataset

Explore preloaded R datasets

```{r}
data()
```

Select Fiji Earthquakes data

```{r}
#load Fiji earthquake data
data(quakes)

#give quakes a shorter, general name (so code chunks can be re-used)
dat <-quakes
```

### Initial data exploration

Quickly summarize each variable
```{r}
summary(dat)
```

### Visualization
######Often, a visual analysis is more helpful than raw data alone. 

Visualize earthquake magnitude with a boxplot. This is the same values as the summary table above, but represented visually.

```{r , echo=FALSE}
boxplot(dat$mag, data = dat , main="Earthquake Magnitude", 
  	ylab="Magnitude")
```


A histogram shows the frequency of a given variable. In this case, earthquake magnitude.
```{r , echo=FALSE}
# histogram of earthquake magnitudes
hist(dat$mag)
```


Graphs are even more helpful when they're visually appealing and well labelled! 
```{r dat, echo=FALSE}
# histogram again, but spruced up
hist(dat$mag, 
     main="Frequency of Earthquake Magnitude Off Fiji", 
     xlab="Magnitude", 
     border="white", 
     col="light blue")
```


